There once was a grid at ol' Carkeek

### 2015-10-07 Manuscript/carkeek_grid.tex
small changes to wording of manuscript; increased MCMC iterations

We modeled the counts of DNA sequences ($Z$) from each of a given taxon $i$, in each replicate PCR $j$, from each replicate of a given location $k$ (hence, $Z_{ijk}$), as though they are ?(proportional to/drawn from)? a Poisson distribution. Poisson distributions are described by one and only one parameter, their mean; in this case the mean is given by an exponential function $e^\lambda$. % WHY IS IT EXPONENTIATED? COUNTS?
Thus,
\begin{equation}\label{some_cool_eqn_name}
	Z_{ijk} \sim Poisson(e^{\lambda_{ijk}})
\end{equation}

@@

%--------------------------------CONTRIBUTIONS----------------------------------
\section*{Author Contributions}
Conceived and designed the experiments: .
Collected the data: .
Conducted the analyses: .
Wrote the first draft: .
Edited the manuscript: .

>>>>

We modeled the counts of DNA sequences ($Z$) from each of a given taxon $i$, in each replicate PCR $j$, from each replicate of a given location $k$ (hence, $Z_{ijk}$), as though they are ?(proportional to/drawn from)? a Poisson distribution. A Poisson distribution is described by one and only one parameter, $\lambda$, which is equal to both the mean and variance. Because in this case our modeled values are discrete counts, we use the natural exponent, $e^\lambda$. % WHY IS IT EXPONENTIATED? COUNTS?
Thus,
\begin{equation}\label{some_cool_eqn_name}
	Z_{ijk} \sim Poisson(e^{\lambda_{ijk}})
\end{equation}

@@

%--------------------------------CONTRIBUTIONS----------------------------------
\section*{Author Contributions}
Conceived and designed the experiments: James L. O'Donnell, Ryan P. Kelly, A. Ole Shelton.
Collected the data: James L. O'Donnell, Greg Williams, Natalie C. Lowell, Ryan P. Kelly, A. Ole Shelton, .
Conducted the analyses: .
Wrote the first draft: .
Edited the manuscript: .
